\begingroup 
\renewcommand{\section}[2]{\anonsection{Список литературы}}
\begin{thebibliography}{00}

    \bibitem{loscut-series}
    Лоскутов А.Ю.
    Анализ временных рядов.
    Курс лекций.
    -- Физический факультет МГУ, 2011. -- 113 с.

    \bibitem{r-mining}
    Шитиков В.К.
    Классификация, регрессия и другие алгоритмы Data Mining
    с использованием R.
    -- Институт экологии Волжского бассейна РАН, 2017. -- 351 с.

    \bibitem{fauler-db}
    Мартин Фаулер.
    NoSQL: новая методология разработки нереляционных баз данных.
    -- Вильямс, 2013. -- 192 с.
    -- ISBN 978-5-8459-1829-1.

    \bibitem{paolella-series}
    Marc S. Paolella.
    Linear Models and Time-Series Analysis.
    -- Wiley, 2019. -- 897 c.
    -- ISBN: 978-1-119-43185-5.

    \bibitem{douglas-series}
    Douglas C. Montgomery.
    Introduction to time series analysis and forecasting.
    -- Wiley, 2015. -- 671 c.

    \bibitem{terence-series}
    Terence C. Mills.
    Applied Time Series Analysis.
    A practical guide to modeling and forecasting.
    -- Academic press, 2019. -- 356 c.
    -- ISBN: 978-0-12-813117-6.

    \bibitem{box-series}
    George Box.
    Time series analysis.
    Forecasting and control.
    -- Wiley, 2016. -- 709 c.
    -- ISBN 978-1-118-67502-1.

    \bibitem{zaki}
    Mohammed J. Zaki.
    Data mining and analysis. //
    Fundamental Concepts and Algorithms.
    -- Cambridge university press, 2014. -- 562 c.
    -- ISBN 978-0521766333.

    \bibitem{ge-series}
    Zhiqiang Ge.
    Multivariate Statistical Process Control.
    -- Springer, 2013. -- 203 c.
    -- ISBN 978-1-4471-4513-4.

    \bibitem{wei-series}
    William W.S. Wei.
    Multivariate Time Series Analysis and Applications.
    -- Wiley, 2019. -- 528 c.

    \bibitem{zhang-series}
    Zhihua Zhang.
    Multivariate Time Series Analysis in Climate
    and Environmental Research.
    -- Springer, 2018. -- 293 c.
    -- ISBN 978-3-319-67339-4.

    \bibitem{tsay-series}
    Ruey S. Tsay.
    Multivariate Time Series Analysis.
    -- Wiley, 2014. -- 522 c.

    \bibitem{nonlinear-series}
    Kamil Feridun Turkman.
    Non-Linear Time Series.
    Extreme Events and Integer Value Problems.
    -- Springer, 2014. -- 255 c.
    -- ISBN 978-3-319-07027-8.

    \bibitem{shumway-series}
    Robert H. Shumway.
    Time Series Analysis and Its Applications.
    With R Examples.
    -- Springer, 2011. -- 202 c.
    -- ISBN 978-1-4419-7864-6.

    \bibitem{rao-series}
    Tata Subba Rao.
    Time Series Analysis: Methods and Applications.
    -- Elsevier, 2012. -- 777 c.
    ISBN: 978-0-444-53858-1.

    \bibitem{mirkin-mining}
    Boris Mirkin.
    Core Concepts in Data
    Analysis: Summarization, Correlation and Visualization.
    -- Springer, 2011. -- 402 c.

    \bibitem{mehmed-mining}
    Mehmed Kantardzic.
    Data mining.
    Concepts, Models, Methods, and Algorithms.
    -- Wiley, 2020. -- 661 c.

    \bibitem{frequent-mining}
    Charu C. Aggarwal.
    Frequent Pattern Mining.
    -- Springer, 2014. -- 85 c.

    \bibitem{han-mining}
    Jiawei Han.
    Data Mining.
    Concepts and Techniques.
    -- Morgan Kaufmann Publishers, 2012. -- 740 c.

    \bibitem{massive-mining}
    Jure Leskovec.
    Mining of Massive Datasets.
    -- Stanford, 2014. -- 513 c.

    \bibitem{clarke-predictive}
    Predictive Statistics.
    Analysis and Inference beyond Models.
    -- Cambridge University Press, 2018. -- 657 c.
    -- ISBN 978-1-107-02828-9.

    \bibitem{kuhn-predictive}
    Max Kuhn.
    Applied Predictive Modeling.
    -- Springer, 2013. -- 615 c.
    -- ISBN 978-1-4614-6848-6.

    \bibitem{sutton-reinforcement}
    Richard Sutton.
    Reinforcement learning.
    -- The MIT Press, 2018. -- 548 c.

    \bibitem{mohri-learinig}
    Mehryar Mohri.
    Foundations of Machine Learning.
    -- The MIT Press, 2018. -- 505 c.

    \bibitem{iiot}
    Boyes, Hugh.
    The industrial internet of things (IIoT): An analysis framework.
    -- Computers in Industry, 2018. -- 1-12 c.

    \bibitem{3-paper}
    Jonathan Law.
    Composable models for online Bayesian analysis of streaming data.
    -- Springer Statistics and Computing 28, 2017. -- 1119–1137 c.

    \bibitem{3-pomp}
    E. L. Ionides, C. Bretó, and A. A. King. 
    Inference for nonlinear dynamical systems.
    Proceedings of the National Academy of Sciences of the United States of America, 
    103(49):18438–43, 2006.

    \bibitem{8-paper}
    Sunny Sanyal, Dapeng Wu, and Boubakr Nour.
    A Federated Filtering Framework for Internet of Medical Things.
    IEEE International conference on communications (IEEE ICC 2019).

    \bibitem{adaptive-filter}
    Simon Haykin.
    Adaptive Filter Theory. 
    -- Prentice Hall, 2002.
    -- ISBN 0-13-048434-2.

    \bibitem{pertuberation}
    G. W. Stewart. 
    Matrix perturbation theory. 
    -- Wiley, 1990. -- 234 c.

    \bibitem{krls-t}
    Steven Van Vaerenbergh.
    Kernel Recursive Least-Squares Tracker
    for Time-Varying Regression.
    -- IEE Transactions on neural networks and learning systems, vol. 23, No 8, 2012.

    \bibitem{4-8}
    Paynabar K, Jin J, Agapiou J, Deeds P (2012) Robust Leak Tests for
    Transmission Systems Using Nonlinear Mixed-Effect Models. Journal of
    Quality Technology 44 (3):265-278

    \bibitem{4-9}
    Grasso M, Colosimo BM, Tsung F (2017) A phase I multi-modelling
    approach for profile monitoring of signal data. International Journal of
    Production
    Research
    55
    (15):4354-4377.
    doi:10.1080/00207543.2016.1251626

    \bibitem{4-10}
    Lei Y, Zhang Z, Jin J (2010) Automatic Tonnage Monitoring for Missing
    Part Detection in Multi-Operation Forging Processes. Journal of
    Manufacturing Science and Engineering-Transactions of the Asme 132
    (5). doi:10.1115/1.4002531

    \bibitem{4-12}
    Yang W-A, Zhou Q, Tsui K-L (2016) Differential evolution-based feature
    selection and parameter optimisation for extreme learning machine in tool
    wear estimation. International Journal of Production Research 54
    (15):4703-4721. doi:10.1080/00207543.2015.1111534

    \bibitem{curr}
    Data Mining Curriculum.
    -- ACM SIGKDD Curriculum Committee, 2006. -- 10 c.

    \bibitem{omnicube}
    Сайт компании Omnicube [Электронный ресурс].
    -- Режим доступа: https://www.omnicube.ru/, свободный. -- (01.06.20)

    \bibitem{faust}
    Faust фреймворк [Электронный ресурс]. 
    -- Режим доступа: https://faust.readthedocs.io/en/latest/, свободный. -- (10.05.20)

\end{thebibliography}
\endgroup

\clearpage